---
title: "R Notebook"
output: html_notebook
---

```{r}
library(readr)
library(ggplot2)

```
```{r}
getwd()

```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, fig.width = 8, fig.height = 6)

library(dplyr)
library(plotly)

#system("ls ../input", intern=TRUE)


AA  <- read.csv("affirmative_asylum.csv")

AS <- read.csv("asylum_statistics.csv")

DA <- read.csv("defensive_asylum.csv")

RS <- read.csv("refugee_statistics.csv")

Rsa <- read.csv("refugee_status.csv")

names(AA) <- c("Country" , "2006","2007","2008","2009","2010", "2011", "2012", "2013","2014", "2015")

names(DA) <- c("Country" , "2006","2007","2008","2009","2010", "2011", "2012", "2013","2014", "2015")

names(Rsa) <- c("Country" , "2006","2007","2008","2009","2010", "2011", "2012", "2013","2014", "2015")

AA1 <- AA[AA$Country == "Total",]
AA <- AA[!AA$Country == "Total",]

DA1 <- DA[DA$Country == "Total",]
DA <- DA[!DA$Country == "Total",]

Rsa1 <- Rsa[!Rsa$Country == "Total",]
Rsa <- Rsa[!Rsa$Country == "Total",]


```

```{r, echo=FALSE}
q <- AA[, c(1,2)]
w <- AA[, c(1,3)]
e <- AA[, c(1,4)]
r <- AA[, c(1,5)]
t <- AA[, c(1,6)]
y <- AA[, c(1,7)]
u <- AA[, c(1,8)]
i <- AA[, c(1,9)]
o <- AA[, c(1,10)]
p <- AA[, c(1,11)]
k <- c("Country", "NumberofRefugee", "year" )

q$year <- 2006
names(q) <- k
w$year <- 2007
names(w) <- k
e$year <- 2008
names(e) <- k
r$year <- 2009
names(r) <- k
t$year <- 2010
names(t) <- k
y$year <- 2011
names(y) <- k
u$year <- 2012
names(u) <- k
i$year <- 2013
names(i) <- k
o$year <- 2014
names(o) <- k
p$year <- 2015
names(p) <- k

a <- rbind(q,w,e,r,t,y,u,i,o,p)

s <- as.data.frame(a)

s$year <- as.factor(s$year)

s <- s[!s$NumberofRefugee == "D" & !s$NumberofRefugee == "X" & !s$NumberofRefugee == "-" & !s$NumberofRefugee == "", ]

s$NumberofRefugee <- as.numeric(gsub(",", "" , s$NumberofRefugee))

d <- s





q <- DA[, c(1,2)]
w <- DA[, c(1,3)]
e <- DA[, c(1,4)]
r <- DA[, c(1,5)]
t <- DA[, c(1,6)]
y <- DA[, c(1,7)]
u <- DA[, c(1,8)]
i <- DA[, c(1,9)]
o <- DA[, c(1,10)]
p <- DA[, c(1,11)]
k <- c("Country", "NumberofRefugee", "year" )
q$year <- 2006
names(q) <- k
w$year <- 2007
names(w) <- k
e$year <- 2008
names(e) <- k
r$year <- 2009
names(r) <- k
t$year <- 2010
names(t) <- k
y$year <- 2011
names(y) <- k
u$year <- 2012
names(u) <- k
i$year <- 2013
names(i) <- k
o$year <- 2014
names(o) <- k
p$year <- 2015
names(p) <- k
a <- rbind(q,w,e,r,t,y,u,i,o,p)
s <- as.data.frame(a)
s$year <- as.factor(s$year)
s <- s[!s$NumberofRefugee == "D" & !s$NumberofRefugee == "X" & !s$NumberofRefugee == "-" & !s$NumberofRefugee == "", ]
s$NumberofRefugee <- as.numeric(gsub(",", "" , s$NumberofRefugee))


d1 <- s




q <- Rsa[, c(1,2)]
w <- Rsa[, c(1,3)]
e <- Rsa[, c(1,4)]
r <- Rsa[, c(1,5)]
t <- Rsa[, c(1,6)]
y <- Rsa[, c(1,7)]
u <- Rsa[, c(1,8)]
i <- Rsa[, c(1,9)]
o <- Rsa[, c(1,10)]
p <- Rsa[, c(1,11)]
k <- c("Country", "NumberofRefugee", "year" )
q$year <- 2006
names(q) <- k
w$year <- 2007
names(w) <- k
e$year <- 2008
names(e) <- k
r$year <- 2009
names(r) <- k
t$year <- 2010
names(t) <- k
y$year <- 2011
names(y) <- k
u$year <- 2012
names(u) <- k
i$year <- 2013
names(i) <- k
o$year <- 2014
names(o) <- k
p$year <- 2015
names(p) <- k
a <- rbind(q,w,e,r,t,y,u,i,o,p)
s <- as.data.frame(a)
s$year <- as.factor(s$year)
s <- s[!s$NumberofRefugee == "D" & !s$NumberofRefugee == "X" & !s$NumberofRefugee == "-" & !s$NumberofRefugee == "", ]
s$NumberofRefugee <- as.numeric(gsub(",", "" , s$NumberofRefugee))


d2 <- s


```


## {.tabset}
```{r}

plot1 <- plot_ly(d, x = ~Country, y = ~(NumberofRefugee), color = ~year , type = "bar" ) %>% layout(title = "Rufugees ( affirmative_asylum)" , barmode = 'relative')


plot2 <- plot_ly(d1, x = ~Country, y = ~(NumberofRefugee), color = ~year , type = "bar" ) %>% layout(title = "Rufugees ( Defensive_asylum)" , barmode = 'relative') 

plot3 <- plot_ly(d2, x = ~Country, y = ~(NumberofRefugee), color = ~year , type = "bar" ) %>% layout(title = "Rufugees ( Refugee_status_asylum)" , barmode = 'relative')


```

### Affirmative_asylum_Refugee_count
```{r}
plot1
```

### Defensive_asylum_Refugee_count
```{r}
plot2
```

### Refugee_status_asylum_count
```{r}
plot3
```
```


















































































```{r}
library(forecast)
library(lambda.tools)
library(futile.logger)


do_forecast <- function(country, df, h=2, plot=FALSE) {
  flog.info("[%s] start", country)
  xs <- as.numeric(colnames(df))
  xs <- c(xs, max(xs) + (1:h))
  ys <- as.numeric(df[country,])

  fc <- forecast(ys, h=h)
  if (plot) plot(fc)

  id <- sprintf("%s.%s", country, tail(xs,h))
  data.frame(Id=id, Prediction=as.numeric(fc$mean))
}

df <- read.csv('training.csv', row.names=1)
colnames(df) <- sub('X','', colnames(df), fixed=TRUE)
out <- fold(rownames(df), function(i,acc) rbind(acc, do_forecast(i,df)), NULL)

# write.csv(out, 'submission.csv', row.names=FALSE, quote=FALSE)

```

